### 2022-09-26 main/chapter_context.tex
add some citations and begin sm

Theory is needed to understand experimental data,
and data are needed to improve theoretical models.
For the experimental work of this thesis to be better understood, this chapter
introduces its theoretical and experimental contexts;
Section~\ref{sec:context_sm_and_beyond} presents the current culmination of
theoretical particle physics in the Standard Model, its limitations, and its
possible future directions including supersymmetric ideas, and
Section~\ref{sec:context_atlas} then describes the \atlas\ detector, with whose
data we hope refine the Standard Model into its improved future forms.

@@

The Standard Model is science's best current understanding of Nature's
fundamental objects in their observable behaviours as particles.
It has solid mathematical foundations, and accurately describes the
physics of particle interactions across a very broad domain.
But that domain is bounded, so the Standard Model is not an ultimate theory of
everything and work continues to expand that boundary on both theoretical and
experimental fronts.
We describe the current Standard Model, its limitations and possible future
directions in Section~\ref{sec:context_sm}.

Supersymmetry an idea that has been applied to build plausible alternatives
to the Standard Model, which may explain future experimental discoveries.
Since the main work of this thesis is a search for effects of supersymmetric
phenomena, supersymmetry and the specific supersymmetric models that we study
are presented in Section~\ref{sec:context_susy}.

\subsection{The Standard Model}
\label{sec:context_sm}
\TODO{particle content figure/tables}

$SU\!(3)_C \times SU\!(2)_L \times U\!(1)_Y$

>>>>

\noindent Theory is needed to understand experimental data,
and data are needed to improve theoretical models.
For the experimental work of this thesis to be better understood, this chapter
introduces its theoretical and experimental contexts;
Section~\ref{sec:context_sm_and_beyond} presents the current culmination of
theoretical particle physics in the Standard Model, its limitations, and its
possible future directions including supersymmetric ideas, and
Section~\ref{sec:context_atlas} then describes the \atlas\ detector, with whose
data we hope refine the Standard Model into its improved future forms.

@@

\noindent Our best current understanding of Nature's fundamental objects in
their observable behaviours as particles is encoded in the Standard Model,
which uses solid mathematical foundations to accurately describe the physics
of particle interactions across a broad domain.
But that domain is bounded, so the Standard Model is not an ultimate theory of
everything, and work continues to expand that boundary on both theoretical and
experimental fronts.
The current Standard Model is described in Section~\ref{sec:context_sm},
along with its limitations and possible future directions.

Supersymmetry an idea that has been applied to build plausible alternatives
to the Standard Model which may explain future experimental discoveries.
Since the main work of this thesis is a search for effects of supersymmetric
phenomena, supersymmetry and the specific supersymmetric models that we study
are presented in Section~\ref{sec:context_susy}.

\subsection{The Standard Model}
\label{sec:context_sm}
% \TODO{particle content figure/tables}

The Standard Model is formulated as a quantized gauge field theory with the
symmetry that its Lagrangian is invariant under local operations of the group
\begin{equation}
SU\!(3)_C \times SU\!(2)_L \times U\!(1)_Y
\end{equation}
on its fields.
Here, the subscript $C$

~\cite{
cottingham2007greenwood,
wells2020discovery,
rubakov1999classical,
thomson2013modern
}
